%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Senior Software Engineer} % Job title
{Globant (formerly Pentalog)} % Organization
{France} % Location
{Oct 2024 - Jan 2025} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Led backend (Symfony) and frontend (Angular) refactoring, reducing technical debt by 20\%.}
    \item {Designed reusable core components, accelerating feature development by 30\%.}
    \item {Defined technical roadmaps, enhancing overall system scalability.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Senior Software Engineer} % Job title
{Imedia24 GmbH} % Organization
{Germany} % Location
{March 2024 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Architected migration from Monolith to Microservices, improving scalability and deployment speed.}
    \item {Designed and developed MVP microservices for modular application structure.}
    \item {Created Composer packages and OpenAPI-based services to standardize integrations and enhance reusability across microservices.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Senior Software Engineer \& Solution Architect} % Job title
{ChillChain} % Organization
{UK} % Location
{Sept 2021 - Dec 2023} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Transformed a Laravel application into a Multi-Tenant system, increasing user capacity 3x.}
    \item {Led AWS migration, implementing CI/CD, disaster recovery, and AWS scaling solutions, including auto-scaling groups and serverless optimizations, resulting in a 300\% efficiency boost.}
    \item {Optimized API performance, reducing response times by 40\% via caching and indexing.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Mid-Senior Software Engineer} % Job title
{Hospitality Web Services} % Organization
{Spain} % Location
{Jan 2019 - July 2021} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Engineered robust API integrations, improving data processing speed by 50\%.}
    \item {Developed custom Laravel solutions, enhancing platform performance and UX.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Mid-Senior Software Developer} % Job title
{Dextra Communication} % Organization
{Morocco} % Location
{Jan 2015 - July 2021} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Progressed from Junior to Mid-Senior Developer, leading critical projects.}
    \item {Automated ETL processes, improving data reliability and reducing manual work.}
    \item {Implemented AWS-based data solutions using S3, DynamoDB, and ElasticSearch.}
  \end{cvitems}
}

\end{cventries}
